Supplementary material for: \nA comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-09-25 manuscript/supplementary.Rmd

# Supplementary figures
```{r, results="asis"}
sfigs %>% pmap(dynbenchmark:::plot_fig, ref_type = "sfig") %>% walk(cat)
```

@@

```{r, results="asis"}
stables %>% pmap(dynbenchmark:::show_table, ref_type = "stable") %>% walk(cat)
```

>>>>

# Supplementary figures
```{r, results="asis"}
sfigs %>% pmap(dynbenchmark:::plot_fig, ref_type = "sfig") %>% modify(paste0, "\n\n") %>% walk(cat)
```

@@

```{r, results="asis"}
stables %>% pmap(dynbenchmark:::show_table, ref_type = "stable") %>% modify(paste0, "\n\n") %>% walk(cat)
```
